Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-06-11 final/cleanpaper/pedestrian_forecasting_iros_2017.tex
Do modifications on cleanpaper.

\documentclass[letterpaper,10pt,conference]{ieeeconf}
%\usepackage{times}

\IEEEoverridecommandlockouts 
\overrideIEEEmargins   % Needed to meet printer requirements.
\usepackage[T1]{fontenc}

@@

%The approach presented in \cite{Kitani2012} has been generalized in a variety of ways.
This approach has been generalized in a variety of ways.
For example, time-dependent information, such as traffic signals, are incorporated in \cite{Karasev2016}, by relaxing the Markov property and considering a switched Markov process.
Other generalizations include replacing the finite-state space with a continuous one, and using a Markov jump process in the motion model.
Unfortunately the desired posteriors are difficult to compute in closed form, and as a result a sampling based method.
The resulting accuracy of such methods, which can come at a large computational expense, can only be known in a probabilistic sense in that the error bounds are themselves random variables.
%Moreover, accuracy can come at a large computational expense.
% which is prohibitive during real-time control.

@@

Many have approached pedestrian forecasting by deriving their motion model from interactions between pedestrians using physically motivated methods \cite{Helbing1995,Xu2012}. 
	Several models derive their motion models from \cite{Helbing1995} by incorporating collision avoidance through an interaction potential \cite{Pellegrini2009,Yamaguchi2011,Yi2016}. 
	However this method suffers from not planning for other pedestrian positions at future times. 
	Others take optical flow as input \cite{Hospedales2009,Wang2009,Emonet2011}.
	These approaches use variants of Hierarchical Dirichlet Processes on discretized optical flow to determine temporal motifs (i.e. classes of motion within the scene), or on a Markov model. 
	 These models are not agent based, and the lack of an explicit motion model limits their predictive power. 
	 Recently methods have been developed to predict trajectories by introducing and sampling Anticipatory Temporal Conditional Random Fields which incorporate learned affordances based on observed objectives within the scene \cite{Koppula2016}. 
	 Others create agent-based models based on Gaussian Processes, though they suffer issues when trained on discretized trajectories \cite{Tay2008,Wang2008,Trautman2015}. 
	Most recently a method using Long Short-Term Memory (lstm) to learn pedestrian motion models without making assumptions about the manner in which agents interact is the state-of-the-art algorithm for socially based models and has a rapid computation time \cite{Alahi2016}.

@@

The output distributions of the four algorithms were compared using their integrals over the cells of a regular grid over our domain. 
These integrals are used to visualize the distributions in Figures \ref{fig:bookstore-1-2} and \ref{fig:death-1-2}.
%In keeping with our measurement model, the ground truth compared against was a grid that was identically zero except on a bounding box around the measurement at time $t$. 
%The ground truth bounding box at each time instance were set equal to the average bounding box dimension centered at the 
%were the average bounding box dimensions in the training data set. 
Because our predictions all share the same scale, we amalgamate all of the prediction and truth values for all of the simulated agents at a given time step and generate ROC curves.
In our analysis, we sought a metric that evaluated the utility of prediction algorithms in the autonomous vehicle context. 
	In this instance it is critical that the generated set of predictions contains the ground-truth observed trajectory while including as few false positive detections as possible.
	ROC curves which plot the true positive rate (i.e. the proportion of the ground truth trajectory that is correctly identified) against the false positive rate (i.e. the proportion of the generated set that does not correspond to the ground truth trajectory), evaluate this aforementioned safety criteria for autonomous vehicles exactly. 
	The Area Under the Curve (AUC) is a standard measure of the quality of a predictor.  
	The closer that this AUC is to one, the better the prediction algorithm.
	Figure \ref{fig:auc_vs_time} shows the analysis of the AUC of each algorithm versus time.

	In addition, we evaluated the Modified Hausdorff Distance (MHD) from the ground truth trajectory to a sample from the predictions at each time to provide a geometric measure of how accurate the predictions are. 
	Figure \ref{fig:mhd_vs_time} shows MHD plotted against time.
	Though popular in evaluating the geometric proximity of the ground truth trajectory and a predicted set, it is not the most appropriate way to evaluate the utility of an algorithm in the autonomous vehicle context. 
	Specifically consider the instance of a generated set of predictions which does not contain the ground-truth observed trajectory but is close to the ground-truth trajectory geometrically. 
	If this generated set of predictions was used in the autonomous vehicle context, it would not preclude certain portions of the space where the person was occupying. 
	Notice that the true positive rate would be zero meaning that the generated set of predictions was not useful.
	Whereas the MHD would describe this generated set of predictions as informative.
Our predictor behaves better than any of the other compared methods at moderately large $t$.
%, where we capture the behavior of the agent without suffering the misplaced confidence observed in Kitani et al.'s predictions. 
%Their encoding of velocity results in the prediction lagging behind the actual observed motion. 
This is despite providing the algorithm in \cite{Kitani2012} with the specific final location of each agent.
%Even given significantly better information, Kitani et al. generates lower quality predictions than our algorithm at all time scales.

>>>>

\documentclass[letterpaper,10pt,conference]{ieeetran}
%\usepackage{times}

\IEEEoverridecommandlockouts 
%\overrideIEEEmargins   % Needed to meet printer requirements.
\usepackage[T1]{fontenc}

@@

%The approach presented in \cite{Kitani2012} has been generalized in a variety of ways.
This approach has been generalized in a variety of ways.
For example, time-dependent information, such as traffic signals, are incorporated in \cite{Karasev2016}, by relaxing the Markov property and considering a switched Markov process.
Other generalizations include replacing the finite-state space with a continuous one, and using a Markov jump process in the motion model.
Unfortunately the desired posteriors are difficult to compute in closed form, and as a result use sampling based methods.
The resulting accuracy of such methods, which can come at a large computational expense, can only be known in a probabilistic sense in that the error bounds are themselves random variables.
%Moreover, accuracy can come at a large computational expense.
% which is prohibitive during real-time control.

@@

Many have approached pedestrian forecasting by deriving their motion model from interactions between pedestrians using physically motivated methods \cite{Helbing1995,Xu2012}. 
	Several models derive their motion models from \cite{Helbing1995} by incorporating collision avoidance through an interaction potential \cite{Pellegrini2009,Yamaguchi2011,Yi2016}. 
	However this method suffers from not planning for other pedestrian positions at future times. 
	Others take optical flow as input \cite{Hospedales2009,Wang2009,Emonet2011}.
	These approaches use variants of Hierarchical Dirichlet Processes on discretized optical flow to determine temporal motifs (i.e. classes of motion within the scene), or on a Markov model. 
	 These models are not agent based, and the lack of an explicit motion model limits their predictive power. 
	 Recently methods have been developed to predict trajectories by introducing and sampling Anticipatory Temporal Conditional Random Fields which incorporate learned affordances based on observed objectives within the scene \cite{Koppula2016}. 
	 Others create agent-based models based on Gaussian Processes, though they suffer issues when trained on discretized trajectories \cite{Tay2008,Wang2008,Trautman2015}. 
	Most recently a method using Long Short-Term Memory (LSTM) to learn pedestrian motion models without making assumptions about the manner in which agents interact is the state-of-the-art algorithm for socially based models and has a rapid computation time \cite{Alahi2016}.

@@

The output distributions of the four algorithms were compared using their integrals over the cells of a regular grid over our domain. 
These integrals are used to visualize the distributions in Figures \ref{fig:bookstore-1-2} and \ref{fig:death-1-2}.
%In keeping with our measurement model, the ground truth compared against was a grid that was identically zero except on a bounding box around the measurement at time $t$. 
%The ground truth bounding box at each time instance were set equal to the average bounding box dimension centered at the 
%were the average bounding box dimensions in the training data set. 
Because our predictions all share the same scale, we amalgamate all of the prediction and truth values for all of the simulated agents at a given time step and generate ROC curves.
In our analysis, we sought a metric that evaluated the utility of prediction algorithms in the autonomous vehicle context. 
	In this instance it is critical that the generated set of predictions contains the ground-truth observed trajectory while including as few false positive detections as possible.
	ROC curves which plot the true positive rate (i.e. the proportion of the ground truth trajectory that is correctly identified) against the false positive rate (i.e. the proportion of the generated set that does not correspond to the ground truth trajectory), evaluate this aforementioned safety criteria for autonomous vehicles exactly. 
	In order to generate true positive rate and false positive rate, a probability distribution has to be thresholded to yield a binary map. 
	Each chosen threshold creates a point on the ROC curve. We treat every value of each bounding box as a threshold.
	The Area Under the Curve (AUC) is a standard measure of the quality of a predictor.  
	The closer that this AUC is to one, the better the prediction algorithm. Each method of generating thresholds creates a different AUC, ours in particular corresponds to the AUC variant from \cite{Judd2009}. Figure \ref{fig:auc_vs_time} shows the analysis of the AUC of each algorithm versus time.

	In addition, we evaluated the Modified Hausdorff Distance (MHD) \cite{Dubuisson1994} from the ground truth trajectory to a sample from the predictions at each time to provide a geometric measure of how accurate the predictions are. 
	Figure \ref{fig:mhd_vs_time} shows MHD plotted against time.
	Though popular in evaluating the geometric proximity of the ground truth trajectory and a predicted set, it is not the most appropriate way to evaluate the utility of an algorithm in the autonomous vehicle context. 
	Specifically consider the instance of a generated set of predictions which does not contain the ground-truth observed trajectory but is close to the ground-truth trajectory geometrically. 
	If this generated set of predictions was used in the autonomous vehicle context, it would not preclude certain portions of the space where the person was occupying. 
	Notice that the true positive rate would be zero meaning that the generated set of predictions was not useful.
	Whereas the MHD would describe this generated set of predictions as informative.
Our predictor behaves better than any of the other compared methods at moderately large $t$.
%, where we capture the behavior of the agent without suffering the misplaced confidence observed in Kitani et al.'s predictions. 
%Their encoding of velocity results in the prediction lagging behind the actual observed motion. 
This is despite providing the algorithm in \cite{Kitani2012} with the specific final location of each agent.
%Even given significantly better information, Kitani et al. generates lower quality predictions than our algorithm at all time scales.
